fdcoexist

### 2018-08-25 paper_simulations.Rmd
:memo: Rewrite intra-sp equation + growth term eq.

$$R_{i, x} = k \times \exp\left(- \frac{(trait_i - env_x)^2}{2\times {width}^2}\right)$$

@@

$$
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(trait_i - env_x)^2}{2\times {width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1, j \neq i}^{S} N_{t, j, x} \times (1 - \delta_{ij})
}
$$

NB: When $i$ = $j$, the species faces intra-specific competition leading to:
$$\delta_{ii} = \frac{K}{(K - N_{t,i,x})}$$

@@

$$
N_{t+1, i, x} = \frac{
    k \times \exp\left(- \displaystyle\frac{(trait_i - env_x)^2}{2\times {width}^2}\right) \times N_{t, i, x}}{
    1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
        B \times \displaystyle\sum_{j = 1,~j = i}^{S}\frac{K}{K - N_{t, j, x}}
}
$$

@@

>>>>

$$R_{i, x} = k \times \exp\left(- \frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right)$$

@@

$$
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1, j \neq i}^{S} N_{t, j, x} \times (1 - \delta_{ij})
}
$$

The equation above only considers inter-specific competition when $j \neq i$ in the sum. We can however add intra-specific competition when $j = i$. Each site has a species-specific carrying capacity $K$ as the number of individuals approaches this carrying capacity the intra-specific competition increases:
$$\alpha_{ii} = \frac{K}{K - N_{t,i,x}}$$

@@

$$
N_{t+1, i, x} = \frac{
    k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
    1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
        B \times \displaystyle\sum_{j = 1,~j = i}^{S}\frac{K}{K - N_{t, j, x}}
}
$$

@@

Because several traits participate to the growth term depending on their contribution we can rewrite the growth term as:
$$R_{i, x} = \sum_{g = 1}^T w_g \times k \times \exp\left(- \frac{(\text{trait}_{g,i} - \text{env}_x)^2}{2\times \text{width}^2}\right)$$

with $g$ the trait number, $0 \leq w_g \leq 1$ the contribution of this trait to growth (and $\sum_{g = 1}^T w_g = 1$), $\text{trait}_{g, i}$ the trait number $g$ of species $i$.
